Representable cylindric algebras of dimension $\omega$: the aspects of canonicity

### 2021-07-04 filtration-stuff/NewText.tex
proof for fusions

  \begin{enumerate}
  \item  $\mathcal{M} = \langle W, R, \vartheta \rangle$ be a ${\bf K}5$-model. Consider $\Gamma' = \Gamma \cup \{ \Diamond \Box \psi \: | \: \Box \psi \in \Gamma \}$. Let $\Delta$ be any finite and $\operatorname{Sub}$-closed extension of $\Gamma'$. Then a model $\widehat{M} = \langle W / \sim_{\Delta}, (R^{min}_{\Delta})^{E}, \widehat{\vartheta} \rangle$ is a filtration of $\mathcal{M}$ through $\Delta$.
  \item Let $\mathcal{L} = {\bf K} \oplus \Diamond \Diamond \Diamond p \to \Diamond p$, then we have the similar statement for $\mathcal{L}$, where $\Delta$ is an extension of $\Gamma' = \{ \Diamond \Diamond \psi \: | \: \Diamond \psi \}$.
  \end{enumerate}
\end{lemma}

@@

  \item Let us prove the second item. Let $\mathcal{M}$ be an $\mathcal{L}$-model.
  The $\mathcal{L}$-closure of the minimal filtered relation modulo $\Delta$, namely ${R_{\Delta}^{min}}^{\mathcal{L}}$ has the following form:
  \begin{center}
    ${R_{\Delta}^{min}}^{\mathcal{L}} = \bigcup \limits_{i < \omega} {R_{\Delta}^{min}}^{2i + 1}$
  \end{center}
  Let $\Diamond \psi \in \Delta$, $(\hat{x}, \hat{y}) \in {R_{\Delta}^{min}}^{\mathcal{L}}$, and $\mathcal{M}, y \models \psi$. The base case is self-evident.
  Let $k < \omega$ and $(\hat{x}, \hat{y}) \in {R_{\Delta}^{min}}^{2k + 3}$ and the statement holds for ${R_{\Delta}^{min}}^{2k + 1}$.

\end{enumerate}
\end{proof}

>>>>

  \begin{enumerate}
  \item  $\mathcal{M} = \langle W, R, \vartheta \rangle$ be a ${\bf K}5$-model. Consider $\Gamma' = \Gamma \cup \{ \Diamond \Box \psi \: | \: \Box \psi \in \Gamma \}$. Let $\Delta$ be any finite and $\operatorname{Sub}$-closed extension of $\Gamma'$ that contains all $\Diamond \Box \psi$ for each $\Box \psi \in \Delta$. Then a model $\widehat{M} = \langle W / \sim_{\Delta}, (R^{min}_{\Delta})^{E}, \widehat{\vartheta} \rangle$ is a filtration of $\mathcal{M}$ through $\Delta$.
  \item Let $\mathcal{L} = {\bf K} \oplus \Diamond \Diamond \Diamond p \to \Diamond p$, then we have the similar statement for $\mathcal{L}$, where $\Delta$ is an extension of $\Gamma' = \{ \Diamond \Diamond \psi \: | \: \Diamond \psi \}$ that contains all $\Diamond \Diamond \varphi$ for $\Diamond \varphi \in \Delta$.
  \end{enumerate}
\end{lemma}

@@

  \item Let us prove the second item. Let $\mathcal{M}$ be an $\mathcal{L}$-model.
  The $\mathcal{L}$-closure of the minimal filtered relation modulo $\Delta$, namely ${R_{\Delta}^{min}}^{\mathcal{L}}$ has the following form:
  \begin{center}
    ${R_{\Delta}^{min}}^{\mathcal{L}} = \bigcup \limits_{k < \omega} {R_{\Delta}^{min}}^{2k + 1}$
  \end{center}
  We reformulate this closure equivalently as follows:
  \begin{enumerate}
    \item $R_0 = R_{\Delta}^{min}$
    \item $R_{n + 1} = R_n \cup ((R_{\Delta}^{min})^2 \circ R_n)$
    \item ${R_{\Delta}^{min}}^{\mathcal{L}} = \bigcup \limits_{k < \omega}$
  \end{enumerate}

  The base case is self-evident. Suppose the statement holds for $R_{n}$ and $(\hat{x}, \hat{y}) \in (R_{\Delta}^{min})^2 \circ R_n$, that is, there exists $\hat{z}$ such that $(\hat{x}, \hat{z}) \in (R_{\Delta}^{min})^2$ and $(\hat{z}, \hat{y}) \in R_n$. By IH, we have $\mathcal{M}, z \models \Diamond \varphi$.

  We have the following:

  \xymatrix{
  &&&&&& \hat{x} \ar[r]^{R_{\Delta}^{min}} & \widehat{y_1} \ar[r]^{R_{\Delta}^{min}} & \hat{z}
  }
\end{enumerate}
  The sequence of implications if the following:
  \begin{center}
    $\widehat{\mathcal{M}}, \hat{z} \models \Diamond \varphi \Rightarrow \widehat{\mathcal{M}}, \widehat{y_1} \models \Diamond \Diamond \varphi \Rightarrow \mathcal{M}, x \models \Diamond \Diamond \Diamond \varphi \Rightarrow \mathcal{M}, x \models \Diamond \varphi$
  \end{center}
\end{proof}

### 2021-07-04 problem-5/Text.tex
proof for fusions

    If $x \in {\bf C}_i(rep(a))$, then there exists $y \equiv_i x$ such that $y \in rep(a)$, that is, there exists an atom $b$ such that $y \in \prescript{\omega}{}N_b$ and $l_b(y) \leq a$.
    \item If $x \in rep(d_{ij})$, so there exists an atom $b$ with $x \in \prescript{\omega}{}N_a$ and $l_b(x) \leq d_{ij}$, then $x_i = x_j$, then $x \in D_{ij}$.
    \end{enumerate}
  \end{enumerate}
\end{proof}

@@

\begin{enumerate}
  \item $\exists$ has a winning strategy in $\mathcal{G}_{m}(\mathcal{A})$ ($m < \omega$), then $\exists$ has a winning strategy in $\mathcal{G}_{\omega}(\Pi_U \mathcal{A})$, where $\Pi_U \mathcal{A}$ is the non-principal ultrapower of $\mathcal{A}$ modulo ultrafilter $U$ over $\omega$.
  \item $\exists$ has a winning strategy in $\mathcal{G}_{m}(\mathcal{A})$ (for every $m < \omega$) iff $\mathcal{A}$ is elementarily equivalent to a completely representable cylindric algebra of dimension $\omega$.
\end{enumerate}
\end{theorem}

>>>>

    Let $x \in {\bf C}_i(rep(a))$. We need $x \in (rep(c_i a))$, that is, one needs to find an atom $c$ such that $l_c(x) \leq c_i a$.

    We already know that there exists $y \equiv_i x$ such that $y \in rep(a)$, that is, there exists an atom $b$ such that $y \in \prescript{\omega}{}N_b$ and $l_b(y) \leq a$.

    \item If $x \in rep(d_{ij})$, so there exists an atom $b$ with $x \in \prescript{\omega}{}N_a$ and $l_b(x) \leq d_{ij}$, then $x_i = x_j$, then $x \in D_{ij}$.
    \end{enumerate}
  \end{enumerate}
\end{proof}

@@

\begin{enumerate}
  \item $\exists$ has a winning strategy in $\mathcal{G}_{m}(\mathcal{A})$ ($m < \omega$), then $\exists$ has a winning strategy in $\mathcal{G}_{\omega}(\Pi_U \mathcal{A})$, where $\Pi_U \mathcal{A}$ is the non-principal ultrapower of $\mathcal{A}$ modulo $U$, an ultrafilter over $\omega$.
  \item $\exists$ has a winning strategy in $\mathcal{G}_{m}(\mathcal{A})$ (for every $m < \omega$) iff $\mathcal{A}$ is elementarily equivalent to a completely representable cylindric algebra of dimension $\omega$.
\end{enumerate}
\end{theorem}
